Temporary Trade Barriers: \\ When Will They End?

### 2017-11-11 presentation.tex
update presentation for SEAs

\begin{frame}{Institutional Detail}
\begin{itemize}[<+->]
	\item Temporary trade barriers have potential to be renewed
		\begin{itemize}
			\item For Anti-dumping (AD) duties, initial five year term, renewal for five years
			\item For Safeguards, four then four; much rarer than AD
		\end{itemize}
	\item Authorized by WTO
	\item Agreements / litigation provide a LOT of latitude
	\item In U.S., for AD:
		\begin{itemize}
			\item DOC initiates, determines whether dumping would continue
			\item ITC determines whether injury would recur / continue
		\end{itemize}
\end{itemize}
\end{frame}

@@

\pause
The probability that AD duties gets renewed
\pause
\begin{itemize}[<+->]
	\item increases in lobbying effort
	\item decreases in the MFN tariff
	\item is invariant to the trading partner's tariff
	\item increases in the profitability of the import-competing sector
	\item increases in the strength of the lobby
	\item AD duties: complicated
\end{itemize}
\end{frame}

@@

\begin{frame}{Political Structure}
In Home country (foreign is passive):
\pause
\begin{itemize}[<+->]
	\item Dept. of Commerce / Int'l Trade Commission ($G$)
		\begin{itemize}[<+->]
			\item Can renew AD duties
			\item Susceptible to influence of lobbying, perhaps both direct and indirect
			\item Modeled in reduced form
		\end{itemize}
%\pause
	\item A Single Lobby
		\begin{itemize}
			\item Represents import-competing sector, $X$
		\end{itemize}	
\end{itemize}

@@

\pause
\vskip.2in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumption 1}
\begin{enumerate}
  \pause
	\item $\ga(e,\ta)$ is increasing and concave in $e$ for all $\ta \in \Theta$.
\end{enumerate}
\end{beamerboxesrounded}
\end{frame}

@@

\pause
\vskip.2in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumption 2}
\begin{enumerate}
  \pause
	\item $\ta$ is uniformly distributed on some $\Theta=\left[\underline{\ta},\overline{\ta}\right]$.
\end{enumerate}
\end{beamerboxesrounded}

@@

\pause
\vskip.25in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma 3}
  The probability that $G$ renews AD duties is increasing and concave in lobbying effort $e$ $\left(\text{i.e. } \frac{\partial r}{\partial e} \geq 0, \ \frac{\partial^2 r}{\partial e^2} \leq 0  \right)$.
\end{beamerboxesrounded}

@@

\vskip.2in
\pause
Indirect effect is positive: higher $\tau^{\textit{ad}}$ increases incentive to exert lobbying effort

\vskip.2in
\pause
Magnitudes are not directly comparable
\begin{itemize}
	\item Work in progress: endogenize $\tau^{\textit{ad}}$
\end{itemize}

@@

\pause
Assume $\ga(\cdot,\cdot)$ increases weakly for all $(e,\ta)$ pairs.
\pause
\begin{itemize}[<+->]
	\item $G$ gives more weight to firms' benefit
	\item Lobbying incentives are unchanged
\end{itemize}

\vskip.25in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 4}
  The total probability that $G$ renews AD duties increases when the weighting function shifts up exogenously.
\end{beamerboxesrounded}
\end{frame}

>>>>

\begin{frame}{Institutional Detail}
\begin{itemize}[<+->]
	\item Temporary trade barriers have potential to be renewed
		\begin{itemize}
			\item For anti-dumping (AD) duties, initial five year term, renewal for five years
			\item For safeguards, four then four; much rarer than AD
		\end{itemize}
	\item In U.S., for AD:
		\begin{itemize}
			\item DOC initiates, determines whether dumping would continue
			\item ITC determines whether injury would recur / continue
		\end{itemize}
	\item Authorized by WTO
		\begin{itemize}
			\item Agreements / litigation provide a LOT of latitude
		\end{itemize}
\end{itemize}
\end{frame}

@@

\pause
The probability that AD duties gets renewed
\pause
\begin{itemize}[<+->]
	\item is invariant to the trading partner's tariff
	\item decreases in the MFN tariff
	\item increases in lobbying effort	
	\item increases in the profitability of the import-competing sector
	\item strength of the lobby and AD duties: complicated
\end{itemize}
\end{frame}

@@

\begin{frame}{Political Structure}
In Home country (foreign is passive):
\pause
\begin{itemize}[<+->]
	\item Lobby
		\begin{itemize}
			\item Represents import-competing sector, $X$
		\end{itemize}	
	\item Dept. of Commerce / Int'l Trade Commission ($G$)
		\begin{itemize}[<+->]
			\item Can renew AD duties
			\item Susceptible to influence of lobbying, perhaps both directly and indirectly
			\item Modeled in reduced form
		\end{itemize}
%\pause

\end{itemize}

@@

\pause
\vskip.2in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumptions}
\begin{enumerate}
  \pause
	\item $\ga(e,\ta)$ is increasing and concave in $e$ for all $\ta \in \Theta$.
	\item $\ga(e,\ta)$ is increasing in $\ta$.
\end{enumerate}
\end{beamerboxesrounded}
\end{frame}

@@

\pause
\vskip.2in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Assumption 2}
\begin{enumerate}
  \pause
	\item   The pdf of the induced distribution on $\ga(e,\ta)$ is weakly increasing in $e$.
\end{enumerate}
\end{beamerboxesrounded}

@@

\pause
\vskip.25in
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Lemma}
  The probability that $G$ renews AD duties is increasing and concave in lobbying effort $e$ $\left(\text{i.e. } \frac{\partial r}{\partial e} \geq 0, \ \frac{\partial^2 r}{\partial e^2} \leq 0  \right)$.
\end{beamerboxesrounded}

@@

\vskip.2in
\pause
Indirect effect is ambiguous: higher $\tau^{\textit{ad}}$ can increase or decrease incentive to exert lobbying effort

\vskip.2in
\pause
	The total probability that $G$ renews AD duties only increases if indirect effect is positive / large enough to outweigh direct effect.
\begin{itemize}
	\item Work in progress: endogenize $\tau^{\textit{ad}}$
\end{itemize}

@@

\pause
Assume $\ga(\cdot,\cdot)$ increases weakly for all $(e,\ta)$ pairs
\pause
\begin{itemize}[<+->]
	\item $G$ gives more weight to firms' benefit
	\item Lobbying incentives are muted
\end{itemize}

\vskip.25in
\pause
\begin{beamerboxesrounded}[upper=palette tertiary, shadow=true]{Result 4}
  The total probability that $G$ renews AD duties increases when the weighting function shifts up exogenously if the direct effect dominates.
\end{beamerboxesrounded}
\end{frame}
